Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Reworded Discussion: Limitations

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, so our study is reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables. However, that will also have its own bias and limitations as well, since they would not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.

>>>>

\subsection{Limitations}
One of the main limitations of this work is that our participants might not have interest, or an accurate idea, of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device, but at this time, about ~15\% of the general population own and use wearable devices \cite{Nilsen,WearableStatNews}, which makes our study reflective of the status quo. We believed that getting a representative survey base was a useful endeavor, although we could have easily recruited only wearable device owners or people specifically interested in wearables. However, that will also have its own bias and limitations as well, since they would not reflect the general population. We expect user perceptions to change as rapidly as wearable technologies and the rate of adoption change.
